Wissenschaftliches Arbeiten

### 2014-06-29 paper.tex
Adding another sentence to the dummy item description for clarity
Rewriting the conclusion

The implementation with both XOR and OR combinations still causes issues if one wants to construct bigger than usual bids. To ease the representation \cite{FLBS99} introduces dummy items which makes the use of XOR obsolete. The idea is that any XOR bid $\langle S_1, p_1 \rangle \ XOR \ \langle S_2, p_2 \rangle $ can be converted to the form $\langle S_1 \cup \{d_1\}, p_1 \rangle \ OR \ \langle S_2 \cup \{d_1\}, p_2 \rangle $ where $d_1$ is such a dummy object. Of course all dummy items of one bidder must be separated from the other bidders to prevent manipulation.

@@

In this paper a short overview of social choice theory was given paired with the reasons why it is relevant to computer sciences. Then the main topic of this paper is introduced by showing the differences between non-combinatorial auctions and combinatorial ones. Furthermore the overall motivation behind the topic is presented. Additionally considerations about representation, formalization and algorithmic complexity are given, closing with two real world applications.

>>>>

The implementation with both XOR and OR combinations still causes issues if one wants to construct bigger than usual bids. To ease the representation \cite{FLBS99} introduces dummy items which makes the use of XOR obsolete. The idea is that any XOR bid $\langle S_1, p_1 \rangle \ XOR \ \langle S_2, p_2 \rangle $ can be converted to the form $\langle S_1 \cup \{d_1\}, p_1 \rangle \ OR \ \langle S_2 \cup \{d_1\}, p_2 \rangle $ where $d_1$ is such a dummy object. Each bidder is allowed to introduce such dummy items for the previous substitution. Of course all dummy items of one bidder must be separated from the other bidders' to prevent manipulation.

@@

In this paper a short overview of social choice theory was given, paired with the reasons why it is relevant to computer sciences.
Firstly, this paper introduces the reader to the basics of social choice and its extension to its computational counter part, containing the basic ideas of voting, fair division and auctions.
Then, secondly, the differences between non-combinatorial auctions and combinatorial ones are highlighted and their levels of expressiveness are shown by an example.
Next, some considerations about the representation of combinatorial bids are made, ranging from naive to more sophisticated ones.
Also the whole bidding process was formalized, so that in the next step an analysis of its algorithmic complexity can be demonstrated.
Here, the NP-completeness is argued and some references to optimized algorithms for efficient ``Winner Determination'' are presented.
In the end, two real world applications are discussed, one about spectrum auctions, the other about the American transportation market. Here some outlook to further problems and research are given too.
